Poseidon Adventure

### 2019-06-07 SardinesOnlyatlantisom2SStest.Rmd
use catch bio as input to SS

<!--In this block, `test` was a vector of 0s, meaning the correction run separately and the new correction implemented in `run_truth` are producing the same results:

```{r catchnums-check, eval=FALSE}

# this was run with results in CalCurrent2013_OA_off folder and run_truth_sardines

catchnumfull <- readRDS(file.path(d.name, paste0(scenario.name, "catchnums_corrected.rds")))

catchnum_ss <- catchnumfull %>%
  filter(species == species_ss) %>%
  arrange(time, polygon, agecl)

new_catage <- truth$catch %>%
  arrange(time, polygon, agecl)

test <- catchnum_ss$atoutput - new_catage$atoutput

# test is all 0 so this worked the same way

@@

# note: time output of this file is in days
# what model timestep is this output matching?
plotcatch <- ggplot() +
  geom_line(data=truecatchbio_ss, aes(x=time/365,y=atoutput, color="true catch bio"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

plotcatch <- ggplot() +
  geom_line(data=truecatchbio_ss, aes(x=time/365,y=atoutput, color="true catch bio from txt"),
            alpha = 10/10) +
  geom_point(data=catchbioN_ss, aes(x=yr,y=anncatchB, color="true catch bio from N"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

```{r catchoff}
sardcatchB <- truecatchbio_ss %>%
  mutate(yr = as.integer(time/365))

@@

@@

Check this against true total catch numbers above. Should be the same.

@@

Get composition inputs for SS (survey and fishery catch at age, survey and fishery lengths, survey and fishey weight at age)

@@

Write time series biomass (tons) and catch (numbers) data for SS using `SS_write_ts`:

@@

#Test writing CPUE in biomass
  stocksynthesis.data <- SS_write_ts(ss_data_list = stocksynthesis.data,
                ts_data = list(survObsBiom$atoutput[fish_years],
                  catch_total$catch[catch_total$yr %in% fish_years]),
                CVs = c(CVs$survey,
                        CVs$fishery),
                data_years = list((survObsBiom$time[fish_years]-survey_sample_time)/timestep+1,             fish_years),
            sampling_month = list(rep(survey_month,nyears),
                                rep(fishing_month,nyears)),
                units = c("biomass","numbers"),
                data_type=c("CPUE","catch"),
                fleets = c(2,1))

>>>>

@@

# note: time output of this file is in days
# what model timestep is this output matching?
# rescale catch in biomass time from days to years
truecatchbio_ss$time <- as.integer(truecatchbio_ss$time/365)

plotcatch <- ggplot() +
  geom_line(data=truecatchbio_ss, aes(x=time,y=atoutput, color="true catch bio"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

plotcatch <- ggplot() +
  geom_line(data=truecatchbio_ss, aes(x=time,y=atoutput, color="true catch bio from txt"),
            alpha = 10/10) +
  geom_point(data=catchbioN_ss, aes(x=yr,y=anncatchB, color="true catch bio from N"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

```{r catchoff}

 sardcatchB <- truecatchbio_ss #%>%
# now done above
#   mutate(yr = as.integer(time/365))

@@

PLEASE DON'T USE THIS FOR CCA. We have determined above that catch in numbers from legacy atlantis code, even corrected, is still off by a factor of 2. We leave the info here because this code can be used for atlantis codebases after December 2015.

@@

Check this against true total catch numbers above. Should be the same (and it is, but both are incorrect in the absolute scale due to the CATCH.nc output problem in older codebases).

@@

Get composition inputs for SS (survey and fishery catch at age, survey and fishery lengths, survey and fishey weight at age).

Because catch composition information goes in to the assessment as a proportion, we can use fishery catch at age from this legacy codebase even with absolute catch numbers likely half what they should be overall.

@@

*Now changing catch units to tons!*

Write time series biomass (tons) and catch (tons) data for SS using `SS_write_ts`:

@@

#Test writing CPUE in biomass
  stocksynthesis.data <- SS_write_ts(ss_data_list = stocksynthesis.data,
                ts_data = list(survObsBiom$atoutput[fish_years],
                  truecatchbio_ss$atoutput[truecatchbio_ss$time %in% fish_years]),
                CVs = c(CVs$survey,
                        CVs$fishery),
                data_years = list((survObsBiom$time[fish_years]-survey_sample_time)/timestep+1,             fish_years),
            sampling_month = list(rep(survey_month,nyears),
                                rep(fishing_month,nyears)),
                units = c("biomass","biomass"),
                data_type=c("CPUE","catch"),
                fleets = c(2,1))

### 2019-06-07 docs/index.Rmd
use catch bio as input to SS

<a href="https://sgaichas.github.io/poseidon-dev/SardinesOnlyatlantisom2SStest.html" target="_blank">Start on Sardines in the CalCurrent, all true and SS data, May 31, 2019, updated June 5</a>

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/SardinesOnlyatlantisom2SStest.html" target="_blank">Sardines in the CalCurrent run with F and rec dev scenario, all true and SS data, May 31, 2019, updated June 7</a>
